---
title: "Sneh_Patel_Assignment2.4"
author: "Sneh Patel"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bayesrules)
library(tidyverse)
```

# Exercise 3.11

## Prior Distribution

The prior distribution is:

pi ~ Beta(3, 9)

```{r}
plot_beta(3, 9)
```

## Posterior Distribution

Given data: 15 out of 50 students are regular bike riders.

The posterior distribution is:

pi ~ Beta(18, 44)

```{r}
plot_beta(18, 44)
```

## Posterior Summary

Mean = 0.29 (approximately)  
Mode = 0.283 (approximately)  
Standard Deviation = 0.058 (approximately)  

The posterior distribution is closer to the observed data (0.30) than the prior (0.25). This shows that the data has a stronger influence due to a reasonably large sample size.

---

# Exercise 3.18

## Patrick

Prior: Beta(3,3)  
Data: 30 out of 40  

```{r}
summarize_beta_binomial(3, 3, 30, 40)
plot_beta_binomial(3, 3, 30, 40)
```

---

## Harold

Prior: Beta(3,3)  
Data: 15 out of 20  

```{r}
summarize_beta_binomial(3, 3, 15, 20)
plot_beta_binomial(3, 3, 15, 20)
```

---

## Comparison

Patrick’s posterior distribution is more concentrated because of a larger sample size (40 observations). Harold’s posterior is more spread out due to fewer observations (20). 

Both have similar proportions, but Patrick’s result is more reliable since it is based on more data.

---

# AI Usage

I used ChatGPT to assist with understanding Bayesian updating, deriving the Beta distributions, and generating R code. I verified the results before submission.